An example of extremely reproducible enrichment analysis

### 2023-12-14 manuscript/example_pub.Rmd
adding example scipt to manuscript folder; this generates PDF figures for the journal article

@@

@@

@@

@@

v1 <- list("ORA up"=ora_ups, "FCS up"=fgsea_ups)
v2 <- list("ORA dn"=ora_dns, "FCS dn"=fgsea_dns)
par(mar=c(10,10,10,10))
par(mfrow=c(2,1))
plot(euler(v1),quantities = list(cex = 2), labels = list(cex = 2))
plot(euler(v2),quantities = list(cex = 2), labels = list(cex = 2))

>>>>

pdf("fig5a.pdf",width=5,height=5)
plot(mds, xlab="Coordinate 1", ylab="Coordinate 2",
  xlim=c(XMIN,XMAX),ylim=c(YMIN,YMAX),
  pch=19,cex=2,col=cols, main="MDS plot")
text(cmdscale(dist(t(mx))), labels=colnames(mx) )
dev.off()

@@

pdf("fig5b.pdf",width=5,height=5)
plot(log10(def$baseMean) ,def$log2FoldChange,
  cex=0.6,pch=19,col="darkgray",
  main="5-azacitidine treatment in AML3 cells",
  xlab="log10(basemean)",ylab="log2(fold change)")
points(log10(sigf$baseMean) ,sigf$log2FoldChange,
  cex=0.6,pch=19,col="red")
mtext(HEADER)
dev.off()

@@

pdf("fig5c.pdf",width=7,height=5)
barplot(c(topdn2,topup2),
  horiz=TRUE,las=1,cex.names=0.65,col=cols,
  main="top DE Reactomes",
  xlab="ES",
  cex.main=0.9)
mtext("ORA test")
dev.off()

@@

pdf("fig5d.pdf",width=5,height=5)
barplot(c(fgsea_dn_vec,fgsea_up_vec),
  horiz=TRUE,las=1,cex.names=0.65,col=cols,
  main="top DE Reactomes",
  xlab="ES",
  cex.main=0.9)
mtext("FCS test")
dev.off()

@@

v1 <- list("ORA up"=ora_ups, "FCS up"=fgsea_ups)
v2 <- list("ORA dn"=ora_dns, "FCS dn"=fgsea_dns)
par(mar=c(10,10,10,10))
par(mfrow=c(2,1))
pdf("fig5e.pdf",width=6,height=5)
plot(euler(v1),quantities = list(cex = 2), labels = list(cex = 2))
plot(euler(v2),quantities = list(cex = 2), labels = list(cex = 2))
dev.off()
